### 2022-07-13 ms/ms.rmd
Writing

We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates. These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimatization") given that acclimation responses are expected to depend both on how long chronic temperature exposure occurs (longer exposure = better acclimation response) and whether exposure took place in the wild ("acclimatized") or lab ("acclimated") [@Seebacher2015]. We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015 show that these factors can impact $Q_{10}$ estimates. Physiological rate measures varied widely across the studies but could generally be grouped into discrete trait categories [@Seebacher2015]. As such, using the detailed information on the trait type and its associated units from a given study we categorized each effect size into one of

>>>>

We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates. These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimatization") given that acclimation responses are expected to depend both on how long chronic temperature exposure occurs (longer exposure = better acclimation response) and whether exposure took place in the wild ("acclimatized") or lab ("acclimated") [@Seebacher2015]. We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015 show that these factors can impact $Q_{10}$ estimates. Physiological rate measures varied widely across the studies but could generally be grouped into discrete trait categories [@Seebacher2015]. As such, using the detailed information on the trait type and its associated units from a given study we categorized each effect size into one of 12 trait categories. These categories included measures of whole organism performance measures including cardiac (i.e., 'cardiac') and muscle ('muscle') function, sprint speed ('sprint') and endurance ('endurance') and metabolic rates (i.e., maximal and resting metabolic rate; max MR', 'rest MR', respectively). Studies also quantified various enzymatic reaction rates, including enzymes involved in general metabolic responses (categorized as 'metabolic enzyme'), various parts of the electron transport chain, including ATPase activity ('ATPase'), mitochondrial leak ('mito_leak') and oxidation ('mito_oxidation') as well as antioxidant enzymes ('antiox'). All other traits not falling within these categories were placed into 'other'.

### *Climate Data*

To understand how climate impacts physiological acclimation abilities we used latitudes and longitudes reported in studies to extract temperature data from terrestrial and aquatic environments. Only studies on wild populations were used for climate analyses because temperature data at locations was likely reflective of past climate history. Temperature data was extracted using the ERA5 climate model. We extracted data over a 30 year period (1958-2022) for each population and species in the data.
